Status and Best Practices for Reproducible Research In Plant Pathology

### 2018-06-01 README.rmd

> Authors, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for 'Status and Best Practices for Reproducible Research In Plant Pathology'_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/10.5281/zenodo.1250665>

@@

### The external files

Much of the collaborative work was done outside of GitHub and R using Google
Sheets. You can view the
[article notes](https://drive.google.com/open?id=19gXobV4oPZeWZiQJAPNIrmqpfGQtpapXWcSxaXRw1-M)
that we collected in the "article_evaluations" tab. Where "template" and
"article_notes" are used in creating that tab and are explained the "Assigning
Articles" vignette of this R package.

@@

**Text and figures :**  [CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/)

@@

### Contributions

We welcome contributions from everyone. Before you get started, please see our [contributor guidelines](CONTRIBUTING.md). Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.

>>>>

> Sparks, A.H., Del Ponte, E.M., Everhart, S., Foster, Z.S.L., Grünwald, N., (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for 'Status and Best Practices for Reproducible Research In Plant Pathology'_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/10.5281/zenodo.1250665>

@@

Code: [MIT](http://opensource.org/licenses/MIT) year: `r format(Sys.Date(), "%Y")`, copyright holder: Adam H Sparks

Data: [CC-0](http://creativecommons.org/publicdomain/zero/1.0/) attribution requested in reuse

@@

We used [RStudio](http://www.rstudio.com/products/rstudio/) on macOS and Ubuntu
17.10.

@@

Adam H Sparks, Associate Professor, Centre for Crop Health  
University of Southern Queensland  
Toowoomba, Queensland 4350

(+61) (7) 4831 1948   adam.sparks@usq.edu.au
https://staffprofile.usq.edu.au/Profile/Adam-Sparks

### 2018-06-01 inst/paper/Sparks_et_al-main_text.Rmd
Add Sydney to paper file author list

---
title: "Status and Best Practices for Reproducible Research In Plant Pathology"
author: "A. H. Sparks, E. M. Del Ponte, N. J. Grünwald, and Z. Foster"
date: 'Last update: `r Sys.Date()`'
output:
  html_document:
    css: my-style.css
    theme: flatly
    toc: true
    toc_float: 
     collapsed: true
     smooth_scroll: true
  pdf_document: default
  word_document:
    reference_docx: Phytopathology_Style_Reference.docx
csl: phytopathology.csl
bibliography: bibliography.bib
always_allow_html: yes
---

>>>>

---
title: "Status and Best Practices for Reproducible Research In Plant Pathology"
author: "A. H. Sparks, E. M. Del Ponte, S. Everhart, Z.S.L. Foster and N. J. Grünwald"
date: 'Last update: `r Sys.Date()`'
output:
  html_document:
    css: my-style.css
    theme: flatly
    toc: true
    toc_float: 
     collapsed: true
     smooth_scroll: true
  pdf_document: default
  word_document:
    reference_docx: Phytopathology_Style_Reference.docx
csl: phytopathology.csl
bibliography: bibliography.bib
always_allow_html: yes
---
